---
title: "Energy Prices to Industry"
output: 
  html_document: 
    theme: paper
    toc: yes
    number_sections: yes
    df_print: kable
date: "2022-11-23"
editor_options: 
  chunk_output_type: console
---

The following document compares the energy prices to industry between GCAM5.2-India and GCAM 6.0. It then computes the difference of the two prices and saves the resulting file as a CSV.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,cache = T
)
```

```{r}
library(tidyverse)
library(ggsci)
library(DT)
```

## Energy prices to industry in GCAM 5.2

-   Note that in GCAM 5.2 only includes the fuel *H2 enduse*. For comparison across versions, it has been renamed to *H2 industrial* here.

```{r}
X5_2prices <- read_delim("5_2prices.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE, skip = 1) %>% 
    pivot_longer(`1990`:`2100`,names_to = "year",values_to = "value") %>% 
select(-c(1,5)) %>% 
  mutate(source="GCAM5.2") %>% 
  mutate(fuel=gsub(fuel,pattern = "H2 enduse",replacement = "H2 industrial"))

datatable(X5_2prices,filter = 'top', options = list(pageLength = 10, autoWidth = TRUE))
```

## Energy prices to industry in GCAM 6

```{r}
# X6prices <- read_delim("6prices.txt", 
#     delim = "\t", escape_double = FALSE, 
#     trim_ws = TRUE, skip = 1) %>% 
#     pivot_longer(`1990`:`2100`,names_to = "year",values_to = "value") %>% 
# select(-c(1,5)) %>% 
#   mutate(source="GCAM6")

X6prices <- read_delim("6prices_wo_ind_adder.txt",
    delim = "\t", escape_double = FALSE,
    trim_ws = TRUE, skip = 1) %>%
    pivot_longer(`1990`:`2100`,names_to = "year",values_to = "value") %>%
select(-c(1,5)) %>%
  mutate(source="GCAM_w/oAdder")


datatable(X6prices,filter = 'top', options = list(pageLength = 10, autoWidth = TRUE))

```

## Energy prices in GCAM 6_new

```{r}
X6Newprices <- read_delim("6_Prices_w_ind_adder.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE, skip = 1) %>% 
    pivot_longer(`1990`:`2100`,names_to = "year",values_to = "value") %>% 
select(-c(1,5)) %>% 
  mutate(source="GCAM6_wAdder")
```

```{r}
# merging the two dataframes 
merging <- bind_rows(X5_2prices,X6prices,X6Newprices)

```

## Comparison of energy prices

```{r, out.width='.8\\textwidth'}
### plotting
ggplot()+
  geom_line(merging %>% filter(year %in% c(2010:2040)),mapping = aes(x=year,y=value,color=source,group=source))+
  facet_wrap(~fuel,scales = "free")+
  theme_bw()+
  scale_color_lancet()+
  theme(axis.text.x = element_text(angle = 90))+
  labs(y="Price (1975$/GJ)",
       x="",subtitle = "Comparison of energy prices to industry in GCAM5.2-India, GCAM 6_raw, and"
        )
```

### Difference in Energy prices to Industry between GCAM 6 and GCAM 5.2-India

```{r}

merging <- left_join(X5_2prices,X6prices,  by= c("year","fuel","region","Units"))
### creating difference
merging_diff <- merging %>% 
  mutate(diff = (value.y-value.x)*-1) %>% 
  mutate(diff=round(diff,4)) %>% 
  select(region,fuel,year,Units,diff)

datatable(merging_diff,filter = 'top', options = list(pageLength = 10, autoWidth = TRUE))

merging_for_gcam <- merging_diff %>% 
  select(-"Units") %>% 
  mutate(`minicam-non-energy-input`="tax") %>% 
  rename(`input-cost`=diff) %>% 
  select(1,2,3,5,4)

write_csv(merging_for_gcam,"fuelPriceDiff.csv")
```
