---
title: "Comparing BEE and BUR emissions data"
author: "Aman Malik"
date: "2022-11-15"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment = FALSE,warning = FALSE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(ggsci)
library(readxl)
library(mgsub)
```

#### BEE data
```{r include=FALSE}
bee_data <- read_excel("BEE_report.xlsx", 
    skip = 1) %>%
  rename_all(~c("variable","category","unit","year","value")) %>% 
  mutate(year= gsub(pattern = "2019-20",replacement = "2019",year)) %>% 
    mutate(year= gsub(pattern = "2030-31",replacement = "2030",year)) 

bau_2030_emissions <- bee_data %>% filter(variable %in% c("Total CO2 emissions","Reduction in CO2 emissions (2030)"),year==2030) %>% 
  pivot_wider(names_from = variable,values_from = value) %>% 
  mutate(`BAU Emissions 2030` = `Total CO2 emissions`+`Reduction in CO2 emissions (2030)`) %>% 
  pivot_longer(cols = 4:6,names_to = "variable") %>% 
  select(4,1,2,3,5)
  
bee_data <- bind_rows(bee_data,bau_2030_emissions) %>% distinct()

```

#### BUR data

```{r, include=FALSE}
bur_all <- read_csv("bur_all_output.csv") %>% 
  select(-1)
```

#### Compare BEE and BUR emissions

```{r,include=FALSE}
bee_data_manp <- bee_data %>% 
  mutate(category = mgsub(category,
                          pattern = c("Pulp and Paper","Thermal Power Plant", "Petroleum Refinery","Petrochemical","Textile","Aluminium","Iron and Steel","Chlor-Alkali"),
                          replacement = c("Pulp & paper", "Electricity production", "Refinery", "Oil & Natural gas", "Textile/leather", "Nonferrous metals", "Iron & steel","Chemicals"))) %>% 
  filter(variable == "Total CO2 emissions") %>% 
  filter(category %in% unique(bur_all$category)) %>% 
  mutate(variable = "Emissions",year = as.character(year))

bur_all_manp <- bur_all %>% 
  mutate(Value= Value/1000,unit = "MtCO2e") %>% 
  select(-5) %>% 
  mutate(variable = "Emissions") %>% 
  select(5,1,3,4,2) %>% 
  rename("year"=Year,"value"=Value) %>% 
  mutate(year=as.character(year))

merged <- bind_rows(bur_all_manp,bee_data_manp)
```
#### Plotting
```{r echo=FALSE}
ggplot()+
  geom_bar(data = bur_all_manp,mapping = aes(x=year,y = value,fill=year),stat = "identity")+
  geom_bar(bee_data_manp,mapping = aes(x=year,y = value,fill=year),stat = "identity",color="black")+
  facet_wrap(.~category,scales = "free")+
  labs(x = "", y = "Emissions (MtCO2e or MtCO2)",subtitle = "Emissions by subsector| data for 2010, 2014, 2016 is from BUR; data for 2019 and 2030 from BEE")+
  scale_fill_lancet()+
  theme_bw()+
  theme(axis.text.x = element_text(size = 6))
```


#### Variables selected

| **BEE**                          | **BUR**                |
|----------------------------------|------------------------|
| Thermal Power Plant              | Electricity Production |
| Iron and Steel                   | Iron and Steel         |
| Distribution Companies (DISCOMs) | NA                     |
| Cement                           | Cement                 |
| Petrochemical                    | Oil and Natural Gas    |
| Petroleum Refinery               | Refinery               |
| Fertilizer                       | Fertilizer             |
| Aluminium                        | Nonferrous metals      |
| Pulp and Paper                   | Pulp and Paper         |
| Chlor-Alkali                     | Chemicals              |
| Textile                          | Textile/leather        |
| Dairy                            | NA                     |
| Sugar                            | NA                     |


#### GAMS data
```{r}
gams_ref_manp <- read_csv(file = "~/CEEW/Carbon Markets/GCAM_results/gcam_ref_manp.csv") %>% select(-1) %>% 
  filter(category %in% unique(bur_all_manp$category)) %>% 
  select(-scenario,-region) %>% 
  mutate(variable="Emissions") %>% 
  rename("unit"=Units) %>% 
  select(variable,category,unit,year,value) %>% 
  filter(year %in% seq(2000,2030,5)) %>% 
  mutate(year=as.character(year)) %>% 
  distinct()

merged <- bind_rows(bur_all_manp,bee_data_manp,gams_ref_manp)
  
```

```{r}
ggplot()+
  geom_bar(data = bur_all_manp %>% mutate(source = "BUR"),mapping = aes(x=year,y = value,fill=source),stat = "identity")+
  geom_bar(bee_data_manp %>% mutate(source = "BEE"),mapping = aes(x=year,y = value,fill=source),stat = "identity")+
  geom_bar(gams_ref_manp %>% mutate(source = "GCAM")  ,mapping = aes(x=year,y = value,fill=source),stat = "identity")+  
  facet_wrap(.~category,scales = "free")+
  labs(x = "", y = "Emissions (MtCO2e or MtCO2)",subtitle = "Emissions by subsector| data for 2010, 2014, 2016 is from BUR; data for 2019 and 2030 from BEE")+
  scale_fill_lancet()+
  theme_bw()+
  theme(axis.text.x = element_text(size = 6))
```

#### Change in emissionn for BEE for different sectors, 2030 compared to 2019
```{r}
bee_data_diff <- bee_data %>% 
  filter(variable == "Total CO2 emissions") %>% 
  pivot_wider(names_from = year,values_from = value) %>% 
  mutate(change = ((`2030`-`2019`)/`2019`)*100)

png("myplot.png", width=8, height=4, units="in", res=300)

ggplot(bee_data_diff)+
  geom_bar(aes(x= reorder(category,+change),y=change,fill = category),stat = "identity",show.legend = F)+
  coord_flip()+
scale_fill_ucscgb()+
  geom_text(aes(category, change,label = round(change,1)),position = position_dodge(width=0.9),
            size=3,vjust=0.5,hjust=1)+
  theme_bw()+
  labs(subtitle =  "Change in emissions (%) in 2030 comp. to 2019",
       x = "",
       y="",caption = "Data from BEE draft report on ICM, 2022"
      )

dev.off()
```
#### Change in emissions in 2030 compared to BAU, BEE
```{r}
bee_data_diff_bau <- bee_data %>% 
  filter(variable %in% c("Reduction in CO2 emissions (2030)","BAU Emissions 2030")) %>% 
  pivot_wider(names_from = variable,values_from = value) %>% 
  mutate(change = (`Reduction in CO2 emissions (2030)`/`BAU Emissions 2030`)*100)

png("myplot2.png", width=8, height=4, units="in", res=300)

ggplot(bee_data_diff_bau)+
  geom_bar(aes(x= reorder(category,+change),y=change,fill = category),stat = "identity",show.legend = F)+
  coord_flip()+
  scale_fill_ucscgb()+
  geom_text(aes(category, change,label = round(change,1)),position = position_dodge(width=0.9),
            size=3,vjust=0.5,hjust=1)+
  theme_bw()+
  labs(subtitle =  "Reduction in CO2 emissions (%) in 2030 rel. to BAU",
       x = "",
       y="",caption = "Data from BEE draft report on ICM, 2022"
      )
dev.off()
```

#### Growth of emissions in BAU in 2030
```{r}
bee_data_growth_bau <- bee_data %>% 
  filter(variable %in% c("Total CO2 emissions","BAU Emissions 2030"))%>%
  filter(!(year== 2030 & variable=="Total CO2 emissions")) %>% 
  mutate(variable= "Emissions") %>% 
  pivot_wider(names_from = year,values_from = value) %>% 
  mutate(change = ((`2030`-`2019`)/`2019`)*100) %>% 
  mutate(source= "BEE")


png("myplot3.png", width=8, height=4, units="in", res=300)

ggplot(bee_data_growth_bau)+
  geom_bar(aes(x= reorder(category,+change),y=change,fill = category),stat = "identity",show.legend = F)+
  coord_flip()+
  scale_fill_ucscgb()+
  geom_text(aes(category, change,label = round(change,1)),position = position_dodge(width=0.9),
            size=3,vjust=0.5,hjust=1)+
  theme_bw()+
  labs(subtitle =  "Growth of emissions (%) in BAU (2019-2030)",
       x = "",
       y="",caption = "Data from BEE draft report on ICM, 2022"
      )
dev.off()
  
```

#### Comparing BEE BAU and GAMS BAU
```{r}
bee_data_growth_bau <- bee_data_growth_bau %>% 
  mutate(category = mgsub(category,
                          pattern = c("Pulp and Paper","Thermal Power Plant", "Petroleum Refinery","Petrochemical","Textile","Aluminium","Iron and Steel","Chlor-Alkali"),
                          replacement = c("Pulp & paper", "Electricity production", "Refinery", "Oil & Natural gas", "Textile/leather", "Nonferrous metals", "Iron & steel","Chemicals")))

gams_ref_manp_growth_bau <- gams_ref_manp %>% 
  filter(year %in% c("2020","2030")) %>% 
  pivot_wider(names_from = year,values_from = value) %>% 
  mutate(change=((`2030`-`2020`)/`2020`)*100) %>% 
  mutate(source="GCAM")

merge <- bind_rows(bee_data_growth_bau %>% select(-`2019`,-`2030`),gams_ref_manp_growth_bau %>% select(-`2020`,-`2030`))

png("myplot4.png", width=8, height=6, units="in", res=300)

ggplot(merge %>% filter(category %in% intersect(unique(bee_data_growth_bau$category),unique(gams_ref_manp_growth_bau$category))))+
  geom_bar(aes(x= source,y=change,fill = source),stat = "identity",show.legend = F)+
 facet_wrap(.~category)+
  scale_fill_ucscgb()+
  #geom_text(aes(category, change,label = round(change,1)),position = position_dodge(width=0.9),
   #         size=3)+
  theme_bw()+
  labs(subtitle =  "Comparison in growth of Emissions in BAU between GCAM and BEE in 2030 compared to 2020",
       x = "",
       y="change (%)",
       #caption = "Data from BEE draft report on ICM, 2022"
      )
dev.off()
```

