---
title: "GCAMvs.BEE"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    code_folding: hide
    theme: cerulean
date: "2022-11-16"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F,warning = F)
```

```{r}
library(tidyverse)
library(ggsci)
library(DT)
```

### Description of tasks

There are two tasks:

1.  Compare the current and future production and emissions from GCAM and the BEE report.

2.  Prepare a target constraint file for GCAM in 2025 and 2030 for industry sectors based on BEE

### GCAM BAU or Current Policies data
```{r}
### Reading in GCAM data from a BAU/Current policies run
gcamBau <- readxl::read_excel("data/gcamBau2.xls") %>%
 filter(title != "title") %>%
  select(-scenario,-region) %>%
  mutate(across(c(`1990`:`2095`),as.numeric)) %>%
  mutate(across(c(`1990`:`2095`),~round(.,digits = 2))) %>%
  pivot_longer(`1990`:`2095`,names_to = "year",values_to = "value") %>%
  mutate(variable = if_else(Units %in% c("Mt","Mt N", "EJ"), "production", "emissions")) %>%
  mutate(scenario = "BAU_curr_pol") 

DT::datatable(data = gcamBau%>% 
  select(-title))
```

```{r eval=FALSE, include=FALSE}
## aggregating and adding sectors
gcam_wider <- gcam_ref %>%
  select(-share) %>%
  pivot_wider(names_from = sector,values_from = value) %>%
  mutate(`Electricity production`= rowSums(select(., contains("elec_")),na.rm = T)) %>%     mutate(`Transport`= rowSums(select(., contains("trn_")),na.rm = T)) %>%
  mutate(`Cement`=cement) %>%
  mutate(`Aluminium`=alumina) %>%
  mutate(`Agriculture`= `agricultural energy use`) %>%
  mutate(`Chemicals` =  `chemical energy use`) %>%
  mutate(`Mining` = `mining energy use`) %>%
  mutate(`Refinery` = `refining`) %>%
  mutate(`Commercials/Institutional`= `comm others`) %>%
  mutate(`Iron & steel` = `iron and steel`) %>%
  mutate(`Fertilizer`= `N fertilizer`) %>%
  pivot_longer(5:54,values_to = "value",names_to = "category") %>%
  mutate(value=value*3.6667) %>%  ### convert MtC to MtCO2
  mutate(Units="MTCO2") %>%
    distinct()

write.csv(gcam_wider,file = "gcam_ref_manp.csv")

```

### BEE data on production, emissions and targets for different sectors
```{r}
#### Reading in data from BEE report on current and future production, emissions
bee_data <- readxl::read_excel("data/BEE_report.xlsx",
    skip = 1) %>%
  rename_all(~c("variable","sector","unit","year","value")) %>%
  mutate(year= gsub(pattern = "2019-20",replacement = "2019",year)) %>%
    mutate(year= gsub(pattern = "2030-31",replacement = "2030",year))

### Calculating BAU emissions in 2030
bau_2030_emissions <- bee_data %>% filter(variable %in% c("Total CO2 emissions","Reduction in CO2 emissions (2030)"),year==2030) %>%
  pivot_wider(names_from = variable,values_from = value) %>%
  mutate(`BAU Emissions` = `Total CO2 emissions`+`Reduction in CO2 emissions (2030)`) %>%
  pivot_longer(cols = 4:6,names_to = "variable") %>%
  select(4,1,2,3,5)

## Combining the two
bee_data <- bind_rows(bee_data,bau_2030_emissions) %>%
  distinct()

### Adding a column on % reduction in emissions wrt BAU
bee_data_diff_bau <- bee_data %>%
  filter(variable %in% c("Reduction in CO2 emissions (2030)","BAU Emissions")) %>%
  pivot_wider(names_from = variable,values_from = value) %>%
  mutate(value = (`Reduction in CO2 emissions (2030)`/`BAU Emissions`)*100) %>%
  select(sector,year,value) %>%
  mutate(variable = "ChangeWrtBAU",unit="percent")

## Putting it all together
bee_data <- bind_rows(bee_data,bee_data_diff_bau)

DT::datatable(bee_data)
```

```{r}

## Renaming sector names in GCAM data according to BEE data
gcamBau <- gcamBau %>%
  mutate(
    sector = mgsub::mgsub(sector,pattern = c("iron and steel","cement"," N fertilizer", "aluminum", "alumina", "electricityTPP", "refining", "electricity","N fertilizer"),
    replacement = c("Iron and Steel", "Cement", "Fertilizer", "Aluminium", "Aluminium", "Thermal Power Plant","Petroleum Refinery","Thermal Power Plant", "Fertilizer"))
    ) %>%
  select(-title)

```

### Creating constraint file for sectors in GCAM based on BEE targets.

Note that there are two methods for extrapolation - one based on linear extrapolation of the reduction (compared to BAU). Other based on the linear extrapolation of the trajectory.

```{r}

# common sectors in GCAM and BEE
common <- unique(intersect(gcamBau$sector,bee_data$sector))

## Approach 1: Linear extrapolation of the reduction in emissions

target_lin_reduction <- bee_data %>% 
  filter(variable=="ChangeWrtBAU",sector %in% common) %>%
  select(sector,year,value,variable) %>% 
  mutate(year=as.numeric(year)) %>% 
  bind_rows(data.frame(sector = common,year=2020,value = 0,variable = "ChangeWrtBAU")) %>% 
  bind_rows(data.frame(
    sector = rep(common,5),
    year = c(2025,2035,2040,2045,2050),
    value=NA,
    variable= "ChangeWrtBAU")) %>% 
  arrange(year) %>% 
  group_by(sector) %>% 
  select(-variable) %>% 
  mutate(missing = Hmisc::approxExtrap(x = year,y = value,xout = c(2020,2025,2030,2035,2040,2045,2050),method = "linear",na.rm = T,)$y) %>% 
  select(-value) %>% 
   rename("target_percent"=missing) 

final_targets <- left_join(target_lin_reduction %>% mutate(year=as.numeric(year)),gcamBau %>% filter(variable=="emissions",sector %in% common) %>% select(sector,year,value) %>% rename("abs_emiss"=value) %>%  mutate(year=as.numeric(year)),by=c("sector","year")) %>% 
   mutate(value = (100-target_percent)*0.01,
          abs_emiss_target=value*abs_emiss,
          abs_emiss_reduct=abs_emiss-abs_emiss_target)

targets_to_write <- final_targets %>% select(sector,year,abs_emiss_target) %>% rename("value"=abs_emiss_target) %>% 
arrange(sector,year)

readr::write_csv(targets_to_write,"targets_BEE_app1.csv")
DT::datatable(final_targets)

## Approach 2: Based on the linear inter and extrapolation of the resulting trajectory

# Calculating target emissions for GCAM in 2030
target_2030 <- left_join(bee_data %>% filter(variable=="ChangeWrtBAU", sector %in% common) %>% select(sector,year,value,variable) %>% select(-variable) %>% 
                           rename("target_percent"=value),
                      gcamBau %>%
                        filter(variable=="emissions",sector %in% common) %>% select(sector,year,value,variable) %>% select(-variable) %>% rename("abs_emiss"=value),
                      by=c("sector","year")) %>% 
  mutate(value = (100-target_percent)*0.01,
         abs_emiss_target=value*abs_emiss,
         abs_reduction=abs_emiss-abs_emiss_target) %>% 
  select(sector,year,abs_emiss_target) %>%
  rename("value"=abs_emiss_target) %>%
  mutate(year=as.numeric(year))

# creating empty df for additional years
target_missing <- data.frame(
  sector = rep(common,5), 
  year = c(2025,2035,2040,2045,2050), 
  value = NA)
              
# extracting 2020 results for linear interpolation between 2020 and 2030
gcam_2020 <- gcamBau %>%
  filter(year==2020,variable == "emissions",sector %in% common) %>%
  select(-Units,-scenario,-variable) %>%
  mutate(year=as.numeric(year))

# Filling missing years by linear interpolation and extrapolation
fill_missing <- bind_rows(gcam_2020,target_2030,target_missing) %>% 
  arrange(year) %>% 
group_by(sector) %>% 
  mutate(missing = Hmisc::approxExtrap(x = year,y = value,xout = c(2020,2025,2030,2035,2040,2045,2050),method = "linear",na.rm = T)$y) %>% 
  select(-value) %>%
    rename("value"=missing) %>% arrange(sector,year)

readr::write_csv(fill_missing,"targets_BEE_app2.csv")

```

#### Task 1a: Comparing emissions

```{r}
gcam <- gcamBau %>% filter(sector %in% common,variable=="emissions", year %in% c(2015:2050)) %>% select(sector,year,value) %>% mutate(source="GCAM",value=value*3.667)

bee <- bee_data %>% filter(sector %in% common,variable=="Total CO2 emissions")%>% select(sector,year,value)%>% mutate(source="BEE") %>% mutate(source="BEE",year = gsub(year,pattern = 2019,replacement = 2020))

gcam_bee <- bind_rows(gcam,bee) %>% mutate(year=as.numeric(year),source=as.factor(source))

ggplot(gcam_bee)+
  geom_line(mapping = aes(x = year,y=value, group=interaction(sector,source), color=sector,linetype = source))+
  facet_wrap(~sector,scales = "free")+
   scale_color_lancet()+
  labs(x="",
       y= " Emissions (MT CO2)",
       subtitle = "Comparison of Emissions (GCAM NZ vs.BEE)",
       caption = "Note BEE data for 2020 is actually from 2019-20, for 2030 is from 2030-31")+
  theme_bw()+
  theme(axis.text.x = element_text(size = 6))
  
```
#### Task 1b: Comparing production quantities
```{r}
##Comparing Production

gcam <- gcamBau %>% filter(sector %in% common,variable=="production", year %in% c(2015:2045)) %>% select(sector,year,value,Units) %>% mutate(source="GCAM",value=if_else(sector=="Thermal Power Plant",value*277.78,value),Units = if_else(sector=="Thermal Power Plant","TWh",Units)) %>% rename("unit"=Units)

bee <- bee_data %>% filter(sector %in% common,variable=="Production") %>% select(sector,year,value,unit)%>% mutate(source="BEE",year = gsub(year,pattern = 2019,replacement = 2020))

gcam_bee <- bind_rows(gcam,bee)

ggplot(gcam_bee %>% filter(sector!="Petroleum Refinery"))+
  geom_line(mapping = aes(x = year,y=value, group=interaction(sector,source), color=sector,linetype = source))+
  facet_wrap(~sector,scales = "free")+
   scale_color_lancet()+
  labs(x="",
       y= " Production (MT) or TWh",
       subtitle = "Comparison of Production quantity (GCAM NZ vs.BEE)",
       caption = "Note BEE data for 2020 is actually from 2019-20, for 2030 is from 2030-31")+
  theme_bw()+
  theme(axis.text.x = element_text(size = 6))

```
#### Task 2: Comparing trajectories BAU and ETS
```{r}
#Comparing GCAM trajectory before and after targets
## App 1

gcamPlot <- gcamBau %>% filter(variable=="emissions",year<2055) %>% select(year,sector,value,scenario) %>% mutate(year=as.numeric(year))

targetPlot1 <- targets_to_write %>%  mutate(scenario="ETS_App1") %>% select(year,sector,value,scenario)

targetPlot2 <- fill_missing %>%  mutate(scenario="ETS_App2") %>% select(year,sector,value,scenario)

gcamPlot <- bind_rows(gcamPlot,targetPlot1) %>% 
  bind_rows(targetPlot2)

ggplot()+
  geom_line(gcamPlot,mapping=aes(x=year,y=value,color=sector,linetype=scenario))+
  facet_wrap(~sector,scales = "free")+
  theme_bw()+
  scale_color_lancet()+
  labs(x="",
       y="CO2 Emissions (MTC)",
       )+
  theme(axis.text.x = element_text(size = 6))
```
