---
title: "Scenario Comparison"
author: "Aman Malik"
date: "2022-11-16"
output:
  # github_document:
#always_allow_html: true
  html_document:
    toc: yes
    number_sections: no
    toc_float: no
    code_folding: hide
    theme: cerulean
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F,warning = F,fig.width = 10,cache = T)
```

```{r}
library(tidyverse)
library(ggsci)
library(DT)
library(readxl)
library(plotly)
```

Scenarios

1.  No constraint

2.  NZ only

3.  Current Policies (includes NZ + RPS)

4.  Current Policies + ETS (NZ+RPS+ETS)

5.  Current Policies + ETS total (NZ+RPS+ETSAll)

6.  NZ and ETS each (NZ + ETSAll)

NZ + ETS

7.  NZ + ETSeach EScerts carry over

    ```{r}
    main_targets_file <- read_csv("main_targets_file.csv") %>% 
      rename("multiplier"=value) %>% 
      pivot_longer(target_percent:abs_emiss_reduct,names_to = "variable",values_to = "value") %>% 
      filter(sector != "Petroleum Refinery")
    ```

```{r}

ggplot(main_targets_file %>% filter(variable=="target_percent"))+
geom_bar(mapping = aes(x=year,y=value,fill=sector),stat = "identity",position = "dodge")+
  theme_bw()+
  scale_fill_aaas()+
  labs(x="",y= "Reduction targets (%, compared to BAU)")

ggplot(main_targets_file %>% filter(variable =="abs_emiss_reduct"))+
geom_area(mapping = aes(x=year,y=value*3.667,fill=sector))+
  theme_bw()+
  scale_fill_aaas()+
  labs(x="",y= "Absolute emission reductions (MTCO2)")

ggplot(main_targets_file %>% filter(variable %in% c("abs_emiss", "abs_emiss_target")))+
geom_line(mapping = aes(x=year,y=value*3.667,color=sector,linetype=variable))+
  theme_bw()+
  scale_color_aaas()+
  labs(x="",y= "Emissions (MTCO2)")+
  facet_wrap(~sector)

```

```{r}
#Load and Display data from GCAM scenarios
### Using two different query files because of different years
Final_results <- read_excel("Final_results.xls") %>% 
filter(title != "title") %>% 
  mutate(across(c(`1990`:`2095`),as.numeric)) %>%
  mutate(across(c(`1990`:`2095`),~round(.,digits = 2))) %>%
  pivot_longer(`1990`:`2095`,names_to = "year",values_to = "value") %>% 
    filter(year <2055)


Final_results_CP<- read_excel("Final_results_cp+fe.xls") %>% 
filter(title != "title") %>% 
  mutate(across(c(`1990`:`2100`),as.numeric)) %>%
  mutate(across(c(`1990`:`2100`),~round(.,digits = 2))) %>%
  pivot_longer(`1990`:`2100`,names_to = "year",values_to = "value") %>% 
  filter(year <2055) %>% 
  rename("sector" = market)

Final_results_CO2 <- read_excel("Final_results_CO2.xls") %>% 
  mutate(across(c(`1990`:`2095`),as.numeric)) %>%
  mutate(across(c(`1990`:`2095`),~round(.,digits = 2))) %>%
  pivot_longer(`1990`:`2095`,names_to = "year",values_to = "value") %>% 
   filter(year <2055) %>% 
  mutate(sector = "CO2 emissions")
  

all_data <- bind_rows(Final_results,Final_results_CP,Final_results_CO2) %>% 
  separate(col=scenario,into = c("scenario","date"),sep = ",",remove = T) %>% 
  select(-date) %>% 
  mutate(scenario=gsub(x = scenario,pattern = "India_",replacement = "")) %>%  
  mutate(scenario = factor(scenario,levels = c("No_constraint",
                                               "NZ",
                                               "NZ+RPO",
                                               "NZ+RPO+ETS",
                                               "NZ+RPO+ETSAll",
                                               "NZ+ETS",
                                               "NZ+ETSAll")))


                                              

```

#### Total emissions

```{r}
tot_em <- all_data %>% filter(sector == "CO2 emissions") 
#%>% filter(scenario %in% c("NZ","NZ+RPO","NZ+RPO+ETSAll"))

a <- ggplot()+
  geom_line(tot_em %>% filter(year>2010),mapping = aes(x = year,y = value*3.667,color=scenario,group=scenario))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y="Total Emissions (MTCO2)")
a
ggplotly(a)
```

#### CO2 emissions by ETS sector and scenario

```{r}
em_sec <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T)) %>% 
  mutate(value=if_else(scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll","NZ+ETS","NZ+ETSAll"),value/2,value))
#%>%filter(scenario %in% c("NZ","NZ+RPO","NZ+RPO+ETSAll"))

p <- ggplot(em_sec %>% filter(sector!="refining",year>2010))+
  geom_line(mapping = aes(x = year,y = value*3.667,group=scenario,color=scenario))+
#  geom_point(mapping = aes(x=year,y=value,group = scenario,shape=scenario,color=scenario))+
  facet_wrap(~sector,shrink = T,scales = "free")+
  scale_color_lancet()+
  theme_bw()+
  labs(x="",y="Emissions (MTCO2)")+
 theme(axis.text.x = element_text(size = 6)) 

 ggplot(em_sec %>% filter(sector!="refining",year>2010,scenario %in% c("NZ","NZ+RPO","NZ+RPO+ETSAll","NZ+ETSAll")))+
  geom_line(mapping = aes(x = year,y = value*3.667,group=scenario,color=scenario))+
#  geom_point(mapping = aes(x=year,y=value,group = scenario,shape=scenario,color=scenario))+
  facet_wrap(~sector,shrink = T,scales = "free")+
  scale_color_lancet()+
  theme_bw()+
  labs(x="",y="Emissions (MTCO2)")+
 theme(axis.text.x = element_text(size = 6)) 

p
ggplotly(p)

```

#### Electricity generation by source

```{r}
elec_gen <- all_data %>% filter(title=="elec gen by subsector")

u <- ggplot(elec_gen %>% filter(!sector %in% c("refined liquids","geothermal","hydro"),year>2010))+
  geom_line(mapping = aes(x = year,y = value,group=scenario,color=scenario))+
 # geom_point(mapping = aes(x=year,y=value,group = scenario,shape=scenario,color=scenario))+
  facet_wrap(~sector,shrink = T,scales = "free")+
  scale_color_lancet()+
  theme_bw()+
  labs(x="",y="Electriicty generation by source (EJ)")+
 theme(axis.text.x = element_text(size = 6))

u
ggplotly(u)


```

#### Share of electricity generation by source

```{r}
r <- ggplot(elec_gen %>% filter(!sector %in% c("refined liquids","geothermal","hydro"),year>2010))+
  geom_bar(mapping = aes(x=year,y=value,fill=sector),stat = "identity",position = "fill")+
  facet_wrap(.~scenario)+
    scale_fill_jama()+
  theme_bw()+
  labs(x="",y="Share of electriicty generation by source")+
 theme(axis.text.x = element_text(size = 6))
r
ggplotly(r)
  
```

#### CO2 prices

```{r}
Cprices <- all_data %>% filter(title=="CO2 prices") %>% 
  mutate(value=value/1.98,value=value/3.667,Units = "2020$/tCO2") # inflation adjusted, 2020 USD;converting carbon price from USD/tC to USD/tCO2



w <- ggplot(Cprices %>% filter(sector!="refining",year>2010))+
  geom_line(mapping = aes(x = year,y = value,group=sector,color=sector))+
#  geom_point(mapping = aes(x=year,y=value,group = scenario,shape=scenario,color=scenario))+
  facet_wrap(~scenario,shrink = T)+
  scale_color_lancet()+
  theme_bw()+
  labs(x="",y="CO2 Price (2020$/tCO2)",)+
 coord_cartesian(ylim = c(0,500))+
 theme(axis.text.x = element_text(size = 6)) 

ggplot(Cprices %>% filter(sector!="refining",year>2010,scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll")))+
  geom_line(mapping = aes(x = year,y = value,group=sector,color=sector))+
#  geom_point(mapping = aes(x=year,y=value,group = scenario,shape=scenario,color=scenario))+
  facet_wrap(~scenario,shrink = T)+
  scale_color_lancet()+
  theme_bw()+
  labs(x="",y="CO2 Price (2020$/tCO2)",)+
 coord_cartesian(ylim = c(0,500))+
 theme(axis.text.x = element_text(size = 6)) 


w
ggplotly(w)
DT::datatable(Cprices)
```



### Aggregate Final Energy
```{r}
fe <- all_data %>% filter(title == "total final energy by aggregate sector")

k <- ggplot(fe%>% filter(year>2010))+
  geom_line(mapping = aes(x=year,y=value,color=scenario,group=scenario))+
  facet_wrap(~sector)+
   scale_color_lancet()+
  theme_bw()+
  labs(x="",y="Aggregated Final Energy (EJ)",)+
# coord_cartesian(ylim = c(0,2500))+
 theme(axis.text.x = element_text(size = 6))

k
ggplotly(k)

```

### An RPO leads to significant emission reductions, reducing the peak in 2040 by ~ 24%.

```{r}
tot_em <- all_data %>% filter(sector == "CO2 emissions",scenario %in% c("NZ","NZ+RPO"))

a <- ggplot()+
  geom_line(tot_em %>% filter(year>2010),mapping = aes(x = year,y = value*3.667,color=scenario,group=scenario))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y="Total Emissions (MTCO2)")
a
ggplotly(a)

```


### Without additional policies, an RPO alone does nothing to decarbonise the industry sector. 
```{r}
em_sec <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T),scenario %in% c("NZ","NZ+RPO"),sector!="refining") %>% select(-title,-Units,-region) %>% 
  pivot_wider(names_from = scenario,values_from = value) %>% 
  mutate(change=((`NZ+RPO`-`NZ`)/`NZ`)*100)
 
 
blah <- ggplot(em_sec %>% filter(year>2010))+
  geom_line(mapping = aes(x=year,y=change,color=sector,group=sector))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y = "change (%)",subtitle ="Change in emissions (%) | NZ+RPO vs. NZ")
ggplotly(blah)

  


```


```{r}
#Change in emissions NZ+RPO+ETS and NZ+RPO+ETSAll

em_sec <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T),scenario %in% c("NZ+RPO","NZ+RPO+ETS","NZ+RPO+ETSAll"),sector!="refining") %>%
  mutate(value=if_else(scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll","NZ+ETS","NZ+ETSAll"),value/2,value)) %>% select(-title,-Units,-region) %>% 
  pivot_wider(names_from = scenario,values_from = value) %>%
  mutate(change_ets=((`NZ+RPO+ETS`-`NZ+RPO`)/`NZ+RPO`)*100,
         change_etsall=((`NZ+RPO+ETSAll`-`NZ+RPO`)/`NZ+RPO`)*100) %>% 
  select(-c(3:5)) %>% 
  pivot_longer(cols = c(3:4),names_to = "scenario",values_to = "value")

a1 <- ggplot(em_sec %>% filter(year>2010))+
  geom_line(mapping = aes(x=year,y=value,color=sector,group=interaction(sector,scenario),linetype=scenario))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y = "change (%)",subtitle ="Change in emissions compared\n to a NZ + RPO scenario (%)")
    
```

```{r}

# Change in sectoral emissions compared to a NZ scenario (w/o RPO)
em_sec <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T),scenario %in% c("NZ","NZ+ETS","NZ+ETSAll"),sector!="refining") %>%
  mutate(value=if_else(scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll","NZ+ETS","NZ+ETSAll"),value/2,value)) %>% select(-title,-Units,-region) %>% 
  pivot_wider(names_from = scenario,values_from = value) %>%
  mutate(change_ets=((`NZ+ETS`-`NZ`)/`NZ`)*100,
         change_etsall=((`NZ+ETSAll`-`NZ`)/`NZ`)*100) %>% 
  select(-c(3:5)) %>% 
  pivot_longer(cols = c(3:4),names_to = "scenario",values_to = "value")

b1 <- ggplot(em_sec %>% filter(year>2010))+
  geom_line(mapping = aes(x=year,y=value,color=sector,group=interaction(sector,scenario),linetype=scenario))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y = "change (%)",subtitle ="Change in emissions compared \n to a NZ scenario (%)")

library(patchwork)
a1+b1+ plot_layout(guides = 'collect')
    
```

### When  constraint is sector-wide, the electricity sector does bulk of the emission reductions; only sector where reductions are higher than required.

### In the absence of an RPO, the electricity sector shares even a greater burden

```{r}
em_sec1 <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T),scenario %in% c("NZ+RPO","NZ+RPO+ETS","NZ+RPO+ETSAll"),sector!="refining") %>%
  mutate(value=if_else(scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll","NZ+ETS","NZ+ETSAll"),value/2,value)) %>% select(-title,-Units,-region) %>% 
  pivot_wider(names_from = scenario,values_from = value) %>%
  mutate(ETS=`NZ+RPO+ETS`-`NZ+RPO`,
         ETSAll=`NZ+RPO+ETSAll`-`NZ+RPO`) %>% 
  select(-c(3:5)) %>% 
  pivot_longer(cols = c(3:4),names_to = "scenario",values_to = "value")

em_sec1 %>% group_by(year,scenario) %>% summarise(value=sum(value))

a2 <- ggplot(em_sec1 %>% filter(year>2010))+
  geom_line(mapping = aes(x=year,y=value,color=sector,group=interaction(sector,scenario),linetype=scenario))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y = "change (MTCO2)",subtitle ="Change in abs. emissions compared\n to a NZ + RPO scenario (MTCO2)")+
  coord_cartesian(ylim = c(-250,50))

em_sec2 <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T),scenario %in% c("NZ","NZ+ETS","NZ+ETSAll"),sector!="refining") %>%
  mutate(value=if_else(scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll","NZ+ETS","NZ+ETSAll"),value/2,value)) %>% select(-title,-Units,-region) %>% 
  pivot_wider(names_from = scenario,values_from = value) %>%
  mutate(ETS=`NZ+ETS`-`NZ`,
         ETSAll=`NZ+ETSAll`-`NZ`)%>% 
  select(-c(3:5)) %>% 
  pivot_longer(cols = c(3:4),names_to = "scenario",values_to = "value")

b2 <- ggplot(em_sec2 %>% filter(year>2010))+
  geom_line(mapping = aes(x=year,y=value,color=sector,group=interaction(sector,scenario),linetype=scenario))+
  theme_bw()+
    scale_color_lancet()+
  labs(x="",y = "change (MTCO2)",subtitle ="Change in abs. emissions compared\n to a NZ scenario (MTCO2)")+
  coord_cartesian(ylim = c(-250,50))

library(patchwork)
a2+b2+ plot_layout(guides = 'collect')
    

```



### Where are emissions cheapest?

```{r}
em_sec1 <- all_data %>% filter(title %in% grep(x = title, pattern ="emissions by sector",value = T),sector!="refining") %>%
  mutate(value=if_else(scenario %in% c("NZ+RPO+ETS","NZ+RPO+ETSAll","NZ+ETS","NZ+ETSAll"),value/2,value)) %>% select(-title,-Units,-region) %>% 
  pivot_wider(names_from = scenario,values_from = value) %>%
  mutate(`RPO+ETS`=`NZ+RPO+ETS`-`NZ`,
         ETS=`NZ+ETS`-`NZ`,
         ETSAll=`NZ+ETSAll`-`NZ`,
         `RPO+ETSAll`=`NZ+RPO+ETSAll`-`NZ`) %>% 
  select(-(`NZ+ETS`:`NZ`)) %>% 
  pivot_longer(3:6,names_to = "scenario",values_to = "value") 
  
  
Cprices <- all_data %>% filter(title=="CO2 prices") %>% 
  mutate(value=value/1.98,value=value*3.667,Units = "2020$/tCO2") %>% 
  filter(!scenario %in% c("NZ","NZ+RPO")) %>% 
  mutate(scenario=gsub(scenario,pattern = "NZ\\+",replacement = "")) %>% 
  select(sector,year,scenario,value) %>% 
  mutate(sector=mgsub::mgsub(sector, pattern = c("IndiaCO2Alu","IndiaCO2Cement","IndiaCO2Elec","IndiaCO2Fert","IndiaCO2IRSTL"),replacement = c("alumina","cement","electricity","N fertilizer","iron and steel") ))

join <- left_join(em_sec1 %>% filter(!scenario %in% c("ETSAll","RPO+ETSAll")),Cprices %>% filter(!scenario %in% c("ETSAll","RPO+ETSAll"),sector!="all"),by=c("year","scenario","sector")) %>% 
  filter(year>2020) %>% 
  mutate(abatement_cost=-(value.x*value.y),unit="Million dollars") %>% 
  dplyr::group_by(scenario,year,unit) %>% 
  summarise(sum=sum(abatement_cost))

emsec2 <- em_sec1 %>% filter(!scenario %in% c("ETS","RPO+ETS")) %>% 
  group_by(year,scenario) %>% 
  summarise(value=sum(value))
  
Cprices2 <- Cprices %>% filter(!scenario %in% c("ETS","RPO+ETS")) %>% 
  filter(sector!="IndiaCO2")


join2 <- left_join(Cprices2,emsec2,by=c("year","scenario")) %>% 
  filter(year>2020) %>% 
  mutate(sum=-(value.x*value.y),unit="Million dollars") 

total_join <- bind_rows(join %>% select(scenario,year,sum,unit),
join2 %>% select(scenario,year,sum,unit))

ggplot()+
  geom_bar(total_join %>% filter(year<2045),mapping = aes(x = year,y=sum/1000,fill=scenario),stat = "identity",position = "dodge")+
  labs(y="Total mitigation cost (billion 2020USD)",x="")+
  scale_fill_lancet()+
  theme_bw()
 

# jp <- ggplot(join %>% filter(year>2010))+
#   geom_line(mapping = aes(x=year,y=red_per_dollar,group=sector,color=sector))+
#   theme_bw()+
#     scale_color_lancet()+
#   labs(x="",y = "change",subtitle ="Change in CO2 emissions (in thousands) per dollar")
# 
# jp

```
### What is happening to cement production?

```{r}
production <- all_data %>% filter(title %in% grep(title,pattern = "production",value = T))

elec_gen <- all_data %>% filter(title=="elec gen by subsector")
elec_gen <- elec_gen %>% group_by(title,region,scenario,Units,year) %>% 
  dplyr::summarise(value=sum(value)) %>% mutate(sector = "elec gen")

production <- bind_rows(production,elec_gen)

z <- ggplot(production %>% filter(year>2010))+
  geom_line(mapping = aes(x = year,y = value,group=scenario,color=scenario))+
#  geom_point(mapping = aes(x=year,y=value,group = scenario,shape=scenario,color=scenario))+
  facet_wrap(~sector,shrink = T,scales = "free")+
  scale_color_lancet()+
  theme_bw()+
  labs(x="",y="Production (MT or EJ)",)+
# coord_cartesian(ylim = c(0,2500))+
 theme(axis.text.x = element_text(size = 6)) 
z
ggplotly(z)
```


```{r}

feprices <- all_data %>% filter(title == "fuel prices to industry")

ggplot(feprices)+
  geom_line(mapping = aes(x=year,y=value,color=scenario,group=scenario))+
  facet_wrap(~sector)+
  scale_color_lancet()
  

```


